He Said What Now?!: Predicting Interest in the Term *China Virus* by State

### 2020-05-05 Final-Draft.Rmd
knitting doc

### Figure 1
```{r, echo=FALSE, warning=FALSE, fig.align=center}
Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
                        "<br>", "Total Population", total_population))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

@@

### Figure 2
```{r, echo=FALSE, warning=FALSE, fig.align=center}
#########white fig
whitefig <- plot_geo(Finaldata, locationmode = 'USA-states')
whitefig <- whitefig %>% add_trace(
    z = ~percent_white, locations = ~State,
    color = ~percent_white, colors = 'Blues'
  )
whitefig <- whitefig %>% colorbar(title = "% White")
whitefig <- whitefig %>% layout(
    title = 'Percent White Identifying by State', geo=g,legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5))             # put legend in center of x-axis

@@

#### Figure 3

@@

```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}

@@

```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State", x = "Interest in China Virus", y = "Density")

@@

### Figure 5
```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= center}
IAtoMT <- Finaldata %>% select(c(State,ChinaVirusInterest,Day)) %>% filter (State %in% c("IA","ID","IL","LA","MA","MD","ME","MI","MN","MO","MS","MT"))

@@

# Density plots
mcmc_dens_overlay(NR_model, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
```
Compared to the previous model, it looks that our chains are more stable and they have closer peaks.

@@

### 4.3b Posterior Predictive Check 
```{r, echo=FALSE, warning=FALSE}
pp_check(model_3, nreps=50)
```
As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model.

@@

```{r, echo=FALSE, warning=FALSE}
pp_check(complexmod, nreps = 50)
```
Overall all ppchecks tend to have the similar graph because we are assuming a normal relationship on the response variable for all of them.

>>>>

### Figure 1
```{r, echo=FALSE, warning=FALSE, fig.align="center"}
Finaldata$hover <- with(Finaldata, paste(polyname, "<br>","Positive Cases:", positive, "<br>","Negative Cases:", negative,"<br>",
                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor,
                        "<br>", "Total Population", total_population))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

@@

### Figure 2
```{r, echo=FALSE, warning=FALSE, fig.align="center"}
#########white fig
whitefig <- plot_geo(Finaldata, locationmode = 'USA-states')
whitefig <- whitefig %>% add_trace(
    z = ~percent_white, locations = ~State,
    color = ~percent_white, colors = 'Blues'
  )
whitefig <- whitefig %>% colorbar(title = "% White")
whitefig <- whitefig %>% layout(
    title = 'Percent White Identifying by State', geo=g,legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5))             # put legend in center of x-axis

@@

### Figure 3

@@

```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}

@@

```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}
b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State") + labs(fill="State", x = "Interest in China Virus", y = "Density")

@@

### Figure 5
```{r, warning=FALSE, message= FALSE, echo=FALSE, fig.align= "center"}
IAtoMT <- Finaldata %>% select(c(State,ChinaVirusInterest,Day)) %>% filter (State %in% c("IA","ID","IL","LA","MA","MD","ME","MI","MN","MO","MS","MT"))

@@

# Density plots
mcmc_dens_overlay(NR_model, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
```

Compared to the previous model, it looks that our chains are more stable and they have closer peaks.

@@

### 4.3b Posterior Predictive Check 
```{r, echo=FALSE, warning=FALSE}
pp_check(model_3, nreps=50)
```

As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model.

@@

```{r, echo=FALSE, warning=FALSE}
pp_check(complexmod, nreps = 50)
```

Overall all ppchecks tend to have the similar graph because we are assuming a normal relationship on the response variable for all of them.
